\documentclass{article}
\title{Minutes from 17 August}

\usepackage{amsmath}

\begin{document}
\section{Papers referred to}
\begin{enumerate}
	\item Marie-Sarah Lacharite, Brice Minaud. \textbf{Improved Reconstruction Attacks on Encrypted Data Using Range Query Leakage}

	\item \textbf{K-Nearest-Neighbour Search on Encrypted Data} (Not published yet)
	
	\item Rafail Ostrovsky. \textbf{Software Protection and Simulation on Oblivious RAMs}
	
	\item Data structure and algorithms I have learnt during undergraduate.
\end{enumerate}


\section{A new OPE scheme}
\begin{itemize}
	\item The idea is to use `searchable' data structures to pre-process the queries so that the queries do not leak the sets used in 1.
	
	\item TBD: include the images describing the scheme.
	
	\item To think: what does the scheme leak?
\end{itemize}


\section{ORAM}
\begin{itemize}
	\item Confirms that the lower-bound of overhead is indeed $\mathcal{O}(\log{n})$.
	
	\item Question to be answered: is ORAM any similar to OPE in the sense that, in order to hide access pattern, how much overhead does it cost?
\end{itemize}


\section{Syntax of encrypted database}
\begin{itemize}
	\item We can think of database in three levels: a string of zeros and ones in the most abstract form, a database as a set of strings, and a database with all the details.
	
	\item We will formalize syntax on the most abstract form first.
	
	\item Notation (need better names):
	\begin{itemize}
		\item \textbf{Initialise}: $1^\lambda \rightarrow \text{params}^{*}$
		
		\item \textbf{KeyGen}: $1^\lambda \rightarrow \textbf{sk}$
		
		\item \textbf{Enc}: $1^\lambda \times \textbf{sk} \times \textbf{DB} \rightarrow \textbf{EDB}$
		
		\item \textbf{Dec}: $1^\lambda \times \textbf{sk} \times \textbf{EDB} \rightarrow \textbf{DB}$
		
		
		\item \textbf{Q}: $\textbf{DB} \times Q \rightarrow \textbf{DB}$
		
		\item \textbf{encQ}: $1^\lambda \times \textbf{sk} \times Q \rightarrow \textbf{eQ} \times \textbf{iQ}$
		
		\item \textbf{EQ}: $1^\lambda \times \textbf{sk} \times \textbf{EDB} \times \textbf{eQ} \rightarrow \textbf{EDB}$
		
		\item \textbf{DQ}: $1^\lambda \times \textbf{sk} \times \textbf{EDB} \times \textbf{iQ} \rightarrow \textbf{DB}$
	\end{itemize}

	\item TBD: add the commutative diagram and explain how it works.
	
	
\end{itemize}




\end{document}