\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{Minutes from 10 August}

\usepackage{hyperref}

\begin{document}
\section{Papers referred to}
\begin{enumerate}
	\item Benjamin Fuller, Mayank Varia, Arkady Yerukhimovich, Emily Shen, Ariel Hamlin, Vijay Gadepally, Richard Shay, John Darby Mitchell, Robert K. Cunningham. \textbf{SoK: Cryptographically Protected Database Search}
	
	\item David Cash, Paul Grubbs, Jason Perry, Thomas Ristenpart. \textbf{Leakage-Abuse Attacks Against Searchable Encryption
} 

	\item Kellaris G, Kollios G, Nissim K, O'Neill A. \textbf{Generic Attacks on Secure Outsourced Databases}
	
	\item Xiao Shaun Wang, Kartik Nayak, Chang Liu, T-H. Hubert Chan, Elaine Shi, Emil Stefanov, Yan Huang. \textbf{Oblivious Data Structures}
	
	\item Emil Stefanov, Marten van Dijk, Elaine Shi, T-H. Hubert Chan, Christopher Fletcher, Ling Ren, Xiangyao Yu, Srinivas Devadas.
\textbf{Path ORAM: An Extremely Simple Oblivious RAM Protocol}
	
	\item Marie-Sarah Lacharite, Brice Minaud. \textbf{Improved Reconstruction Attacks on Encrypted Data Using Range Query Leakage} (have not read the paper yet but have a rough idea what it is about)
	
	\item A few more papers cited in 1, 2 and 4
	
	\item Related lectures from \url{https://www.youtube.com/playlist?list=PLXF_IJaFk-9ADeshgHXrSfuwPyEMa5qS7}
	
\end{enumerate}


\section{Overview of literature in encrypted searchable databases}
\begin{itemize}
	\item See 1.1. There are three broad types of encrypted searchable databases: legacy, custom inverted index, and custom tree traversal. All of which leaks access pattern.
	
	\item Oblivious approaches does not leak access pattern but the bandwidth blowup is lower-bounded by $\mathcal{O}(\log(n))$.
	
	\item Although documents are encrypted using randomized encryption schemes most of the times, the view of the server is a deterministic copy. So file retrieval reveals the query itself. That also means randomized padding based schemes will not work on OPE, due to 6.
\end{itemize}


\section{ORAM}
\begin{itemize}
	\item ORAM is a potential solution to the encrypted searchable databases problem, but its time complexity is not desirable.
	
	\item Remain to revisit the paper that proves the lower-bound on bandwidth blowup.
\end{itemize}


\section{Attack against OPE}
\begin{itemize}
	\item Counting attack in 2 is already sufficient to recover the entire database given prior distribution.
	
	\item 6 provides a more time-efficient solution and can work without prior information.
	
	\item Have to read the paper before next meeting.
\end{itemize}




\end{document}